---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# zooper

<!-- badges: start -->
<!-- badges: end -->

The goal of `zooper` is to provide functions used in zooplankton community composition analysis, as well as a sample data-set to use with the functions.

The package contains a function called `zoopl()`, which is used to calculate the number of zooplankton per liter in a sample. In the folder **data**, there is a practice data-set called **zoop_data.rda** that may be used with the function. Documentation on the data-set can be found in the folder **man** under **zooper-package.Rd**. 

## Installation

You can install the development version of `zooper` like so:

``` r

devtools::install_github("claireestey", "zooper")

```

## Example

This is a basic example which shows you how to use the function `zoopl` to calculate zooplankton per liter if your raw count of a species was 223 individuals, your sub-sample size was 10 mL, and the volume of water filtered through the trap was 30 L:

```{r example}
library(zooper)
zoopl(count = 223, sample_vol = 20, subsample_vol = 12.5, trap_vol = 30)
```
